---
title: "Getting Started with a new Course"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with a new Course}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Disclaimer
Before every semester when preparing the infrastructure for a new course or for a new version of an existing course, the same tasks have to be carried out. The outline given below gives a few hints and ideas on how this process could be automatized. In what follows, we start with a description of the manual process that is used so far. The second part contains possible ideas for automatisation.


# Assumptions
The course is assumed to be a course consisting of the following components

* course notes
* exercises and solutions
* additional material

The structure of the course should be kept as flexible as possible. Hence, further components such as student projects or homework or term projects should be easily integratable.


# Manual Setup Process
The following steps are taken in the setup process

* Step 1: Start a new RStudio project

```bash
R -e 'usethis::create_project(path = "/Users/pvr/Data/Projects/Github/charlotte-ngs/asmss2022_gh-root/main/asmss2022", rstudio = TRUE)'
```


* Step 2: Add a description file

```{r, eval=FALSE}
usethis::use_description(fields = getOption("charlotte.ngs.description"))
```

This file must be edited and adapted according to the new course. This can be done via

```{r, eval=FALSE}
usethis::edit_file(path = "DESCRIPTION")
```


* Step 3: Licence is added 

```{r, eval=FALSE}
usethis::use_cc0_license()
```


* Step 4: README File is added

```{r, eval=FALSE}
usethis::use_readme_rmd()
```

The README file is the main page of content, not only for the Github page, but also for the website which will be created via `pkgdown`


* Step 5: Git Repository

```{r, eval=FALSE}
usethis::use_git()
```


* Step 6: Setting up the pages for the website

```{r, eval=FALSE}
usethis::use_vignette(name = "course_notes", title = "Course Notes")
usethis::use_vignette(name = "course_exercises", title = "Exercises")
usethis::use_vignette(name = "course_solutions", title = "Solutions")
usethis::use_vignette(name = "course_additional_material", title = "Additional Material")
```


* Step 7: Adding a news site

```{r, eval=FALSE}
usethis::use_news_md()
```


* Step 8: Install package

```{r, eval=FALSE}
devtools::document();devtools::install()
```

* Step 9: Build Site

```{r, eval=FALSE}
pkgdown::build_site()
```

After committing and pushing all the material, the material should be available.


# Automation Steps
